Improving the Replicability of Psychological Science Through Pedagogy

### 2016-09-23 paper/paper.Rmd
eric changes typos

In the current work, we do not address these challenges; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. As we discuss below, these replications may have different interpretations: While some are more direct replications, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, our work provides contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

>>>>

In the current work, we do not address these challenges; instead, our goal is more modest. We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings. We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations. While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work. As we discuss below, these replications may have different interpretations: While some are more direct replications, others differ on theoretically-relevant dimensions. Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly. Even in these cases, however, our work contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
